### 2015-05-14 evaluation.tex
fix

\noindent\textbf{Benchmarks }
%
We evaluate our methodology against \sizeOfBenchmarks drivers taken from the 4.0 Linux kernel. We chose non-trivial drivers from several categories: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. We had to manually model the environment for these drivers, a process that required approximately two months of work.

>>>>

\noindent\textbf{Benchmarks }
%
We evaluate our methodology against \sizeOfBenchmarks drivers from the 4.0 Linux kernel. We chose non-trivial drivers of several types: block; char; ethernet; near field communication (nfc); universal serial bus (usb); and watchdog. For all these drivers, we had to understand their environment and manually model it; this required approximately two months of work.
